### 2019-03-18 thesis_proposal_1/main.tex
abstract done

% Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\keywords{tec, de, monterrey}

@@

\vspace*{.06\textheight}
{\scshape\LARGE \univname\par}\vspace{1.5cm} % University name
\textsc{\Large Masters Thesis}\\[0.5cm]      % Thesis type

\HRule \\[0.4cm]                            % Horizontal line
{\huge \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
\HRule \\[1.5cm]                            % Horizontal line

@@

\emph{Co-advisor and\\Director of Program:} \\
% Supervisor name - remove the \href bracket to remove the link
\href{https://www.medinadora.com/}{\cosupname}
%\cosupname
\end{flushright}
\end{minipage}\\[3cm]

@@

\large \textit{A thesis submitted in fulfillment of the requirements\\ for the degree of
% University requirement text
\degreename}\\[0.3cm]
\textit{in}\\[0.4cm]
% Research group name and department name
\groupname\\\deptname\\[2cm]

@@

The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots \\

>>>>

% Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\keywords{nanotechnology, carbon, nano-wires, electrospinning, NFES}

@@

\vspace*{.06\textheight}
{\scshape\LARGE \univname\par} % University name

\begin{center}
\includegraphics[width=0.15\textwidth]{./Figures/uniLogo.png}
\end{center}

\vspace{0.5cm}
\textsc{\Large Masters Thesis Proposal}\\[0.5cm]      % Thesis type

\HRule \\[0.5cm]                            % Horizontal line
{\huge \bfseries \ttitle\par}\vspace{0.25cm} % Thesis title
\HRule \\[0.5cm]                            % Horizontal line

@@

\emph{Co-advisor and\\Director of Program:} \\
% Supervisor name - remove the \href bracket to remove the link
\href{https://www.medinadora.com/}{\cosupname}
%\cosupname
\end{flushright}
\end{minipage}\\[2cm]

@@

\large \textit{A thesis proposal submitted in fulfillment of the requirements\\ for the degree of
% University requirement text
\degreename}\\[0.3cm]
\textit{in}\\[0.4cm]
% Research group name and department name
\groupname\\\deptname\\[2cm]

@@

Carbon nano-wires are versatile materials composed of carbon chains with a wide range of applications due to their matchless properties in electrical matters. Regardless of the high interest in the implementation of carbon nano-wires in several applications and devices, no feasible processes have been developed to synthesize carbon nano-wires. Carbon nano-wires have been fabricated with the use of a photoresist, but little is known about polymers that can produce more conductive carbon nano-wires after pyrolysis. Various polymer solutions have being tested and measured through near field electrospinning (NFES) and photopolymerization processes; it was found that it is not possible to predict the behaviour of the electrospinning process, so additional properties are to be considered to achieve a stable manufacturing process. The thesis proposal is to analyse the rheology of different polymer solutions to determine if they can be easily electrospun at low voltages and then fabricate nanowires with them. The research process will include the design of polymer solutions that can be electrospun, photopolymerized, and then pyrolyzed into conducting carbon nanowires. The research is intended to engineer a newly designed polymer solution to achieve mass scale manufacturing of carbon nano-wires in a cheap, continuous, simple and reproducible manner. \\
